Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2020-05-07 awipev-CO2.Rmd
Still availability of data

### **Data availability**
The data at one minute frequency were tagged with the following quality flags

+ 1: good data
+ 3: failing the date and time test
+ 4: data not usable according to manufacturer
+ 7: failing the regional range test 
+ 12: failing the spike test (NAs from despike)
+ 13: failing the gradient test
+ 15: instrument not deployed or operated
+ 16: acid flush
+ 99: failing the final visual inspection

@@

s1 <- summary(as.factor(d$pco2_corr_qf))*100/length(d$pco2_corr_qf)
s2 <- summary(as.factor(d$sal_fb_qf))*100/length(d$sal_fb_qf)
s3 <- summary(as.factor(d$sal_insitu_ctd_qf))*100/length(d$sal_insitu_ctd_qf)
s4 <- summary(as.factor(d$temp_fb_qf))*100/length(d$temp_fb_qf)
s5 <- summary(as.factor(d$temp_insitu_11m_qf))*100/length(d$temp_insitu_11m_qf)
# durafet and seafet started later
x <- filter(d, datetime >= "2017-08-29 10:00:00")
#s6 <- summary(as.factor(x$temp_dur_qf))*100/length(x$temp_dur_qf)
s7 <- summary(as.factor(x$ph_dur_qf))*100/length(x$ph_dur_qf)
x <- filter(d, datetime >= "2017-08-24 19:00:00")
s8 <- summary(as.factor(x$phINT_qf))*100/length(x$phINT_qf)
z <- t(bind_rows(s1,s2,s3,s4,s5,s7,s8)) %>%
  as.data.frame() %>%
         rownames_to_column(var = "flag") %>% 
         as_tibble()
labels <- c("Good", "Not usable", "Outside regional range", "Outliers (despike)", 
            "Failed visual inspection", "No data")
#colnames(z) <- c("flag", colnames(d)[-1]) # remove first col name (datetime)
colnames(z) <- c("Flag", "pCO2", "Salinity FerryBox", "In situ salinity", 
                 "Temperature FerryBox", "In situ temperature", "Durafet pH", "seaFET pH")
zz <- pivot_longer(z, -Flag)
p <-  ggplot(data = zz, aes(x = name, y = value, fill = Flag)) +
  geom_bar(position = position_stack(reverse = TRUE), stat="identity", width = 0.3) +
  #scale_y_reverse() +
  #discrete_scale(labels = labels) + 
  coord_flip() +
  geom_text(aes(label=round(value, digits = 0)), position = position_stack(0.5), size = 3) +
  labs(x="", y="", title = "Distribution (%) of quality flags", color = "Quality flag") +
  theme_bw()
p
rm(d)
```

>>>>

### **Data availability**
TO DO: add here an horizontal bar plot showing the percent availability of the data

    + 1: good data
    + 3: impossible date and time test
    + 4: data not usable according to manufacturer (flush mode, zero mode, calibration mode...) 
    + 6: failing the manufacturer range test (not used)
    + 7: failing the regional range test 
    + 12: failing the spike test (NAs from despike)
    + 13: failing the gradient test
    + 15: the instrument was not deployed or operated
    + 99: failing the final visual inspection of the data.

@@

s1 <- summary(as.factor(d$pco2_corr_qf))*100/length(d$pco2_corr_qf)
s2 <- summary(as.factor(d$sal_fb_qf))*100/length(d$sal_fb_qf)
s3 <- summary(as.factor(d$sal_insitu_ctd_qf))*100/length(d$sal_insitu_ctd_qf)
s4 <- summary(as.factor(d$temp_fb_qf))*100/length(d$temp_fb_qf)
s5 <- summary(as.factor(d$temp_insitu_11m_qf))*100/length(d$temp_insitu_11m_qf)
# durafet and seafet started later
x <- filter(d, datetime >= "2017-08-29 10:00:00")
#s6 <- summary(as.factor(x$temp_dur_qf))*100/length(x$temp_dur_qf)
s7 <- summary(as.factor(x$ph_dur_qf))*100/length(x$ph_dur_qf)
x <- filter(d, datetime >= "2017-08-24 19:00:00")
s8 <- summary(as.factor(x$phINT_qf))*100/length(x$phINT_qf)
z <- t(bind_rows(s1,s2,s3,s4,s5,s7,s8)) %>%
  as.data.frame() %>%
         rownames_to_column(var = "flag") %>% 
         as_tibble()
labels <- c("Good", "Not usable", "Outside regional range", "Outliers (despike)", 
            "Failed visual inspection", "No data")
#colnames(z) <- c("flag", colnames(d)[-1]) # remove first col name (datetime)
colnames(z) <- c("Flag", "pCO2", "Salinity FerryBox", "In situ salinity", 
                 "Temperature FerryBox", "In situ temperature", "Durafet pH", "seaFET pH")
zz <- pivot_longer(z, -Flag)
p <-  ggplot(data = zz, aes(x = name, y = value, fill = Flag)) +
  geom_bar(position = position_stack(reverse = TRUE), stat="identity", width = 0.3) +
  #scale_y_reverse() +
  discrete_scale(labels = labels) + 
  #coord_flip() +
  geom_text(aes(label=round(value, digits = 0)), position = position_stack(0.5), size = 3) +
  labs(x="", y="", title = "Distribution (%) of quality flags", color = "Quality flag") +
  theme_bw()
p
rm(d)
```
